Bipartite Fidelity and Loschmidt Echo of Bosonic Conformal Interface

### 2017-06-19 compact_boson.tex
[draft] PP_echo, DDDD_echo .py changed, new data for DDDD and PPPP added,
[draft] Punctuation checked, may double check the following eqs. ([draft] Punctuation checked, double check the following eqs. (39), (C3), below (C12), (C27), (D9) .

\todo[inline]{say intuition why not matter, mention application to Laughlin, etc.}

Our derivation follows the general multi-component Boson constraints in Ref.~\onlinecite{affleck_quantum_2001,oshikawa_boundary_2010}. A review of the detailed parameterization of the states can be found in Ref.~\onlinecite{sakai_entanglement_2008}.

\subsection{Mode Expansion of Compact Boson}
Suppose the boson is compactified as $\phi =  \phi + 2\pi R$, using the notation in Ref.\onlinecite{di_francesco_conformal_1997}, we have the following mode expansion 
\begin{widetext}
\begin{equation}
\label{eq:boson-mode-exp}
\begin{aligned}
\phi( z, \bar{z}) = &\phi_0 -i \left( \frac{n}{4\pi g  R} + \frac{m R }{2} \right)  \ln z + \frac{i}{\sqrt{4\pi g}} \sum_{n\ne 0 } \frac{a_n}{n} z^{-n } -i \left( \frac{n}{4\pi g R} - \frac{m R }{2} \right)  \ln \bar{z} + \frac{i}{\sqrt{4\pi g}} \sum_{n\ne 0 } \frac{\bar{a}_n}{n} \bar{z}^{-n } 
\end{aligned}
\end{equation}\end{widetext}
where $n,m$ are momentum and winding modes quantum numbers.

In Ref.\onlinecite{di_francesco_conformal_1997}, the quantization is performed on an equal time space. The boundary state we need here however lives on $x = 0$ -- a equal-space slice. We therefore exchange compact the theory in time direction with period $T$, and identify the holomorphic and anti-holomorphic coordinates as 
\begin{equation}
\label{eq:zzbar}
z = \exp( 2 \pi i \frac{t - x}{L}) \qquad \bar{z} = \exp( 2 \pi i \frac{t + x}{L})
\end{equation}
This corresponds to exchange the $x$ and $t$ in Ref.\onlinecite{di_francesco_conformal_1997}.

We further identify
\begin{equation}
\begin{aligned}
  a_0 &= \sqrt{ 4 \pi g } \left( \frac{n}{4\pi g R} + \frac{m R }{2} \right) \\
   \bar{a}_0 &= \sqrt{ 4 \pi g } \left( \frac{n}{4\pi g R} - \frac{m R }{2} \right)
  \end{aligned}
\end{equation}
to obtain the expression uniform for all the modes
\begin{equation}
\begin{aligned}
i \partial_z \phi =  \sum_n \frac{1}{\sqrt{4\pi g}} a_n z^{-n-1} 
\end{aligned}
\end{equation}

@@

We recall that the gluing condition is written as
\begin{equation}
\begin{aligned}
\label{eq:def_S_in_app}
\begin{pmatrix}
\partial_+\phi^1\\
\partial_-\phi^2
\end{pmatrix}
=S(\theta)
\begin{pmatrix}
\partial_-\phi^1\\
\partial_+\phi^2
\end{pmatrix}
\end{aligned}
\end{equation}
Upon folding $\phi^2$ to the negative axis, its $\partial_x$ derivative becomes $-\partial_x$, so 
\begin{equation}
\begin{bmatrix}
\partial_{+} \phi^1 \\
\partial_{+} \phi^2 \\
\end{bmatrix}
 = S
\begin{bmatrix}
\partial_{-} \phi^1 \\
\partial_{-} \phi^2 \\
\end{bmatrix}
\end{equation}
In terms of the holomorphic coordinates defined in Eq.~\eqref{eq:zzbar}, 
\begin{equation}
\partial_{+} = \frac{4\pi i }{T} \bar{z} \partial_{\bar{z}} \qquad \partial_{-} = -\frac{4\pi i }{T} z\partial_{z}
\end{equation}
the $S$ matrix establish a relation between the modes
\begin{equation}
\begin{aligned}
\label{eq:def_S_in_app_2}
\sum_{n\in\mathbb{Z}}
\begin{pmatrix}
\bar{a}_n^1\bar{z}^{-n}\\
\bar{a}_n^2\bar{z}^{-n}
\end{pmatrix}
= -S(\theta)
\sum_{n\in\mathbb{Z}}
\begin{pmatrix}
a_n^1{z}^{-n}\\
a_n^2{z}^{-n}
\end{pmatrix}
\end{aligned}
\end{equation}
At the boundary $x = 0$ $\bar{z}=z^{-1}$, therefore we have
\begin{equation}
\begin{aligned}
a^i_n + (S^{-1}_{ij})\bar{a}^j_{-n}=0
\end{aligned}
\end{equation}
The solution of the $n \ne 0$ constraints is exactly the boundary state in Eq.~\eqref{eq:bd_state}.

We specialize to $S = S_1$ to solve the $ n = 0$ constraint. We introduce the compactification lattice and its dual\cite{affleck_quantum_2001,oshikawa_boundary_2010}
\begin{equation}
\label{eq:lattice}
\vec{M} = (m_1 2 \pi R_1, m_2 2\pi  R_2)^\top, \quad  \vec{M}^* = (\frac{n_1}{R_1}, \frac{n_2}{R_2})^\top
\end{equation}
to rewrite the zero mode part as 
\begin{equation}
  a_0^i - S^{-1} _{ij} \bar{a}_{0}^j = 0 \,\, \implies \,\, ( \vec{M} + \frac{1}{g}\vec{M}^* ) = S_1 ( -\vec{M} + \frac{1}{g}\vec{M}^* )
\end{equation}
which is basically the multi-component boson winding constraints given in \onlinecite{affleck_quantum_2001,oshikawa_boundary_2010}. The solution gives the interface parameter $\lambda$
\begin{equation}
\begin{aligned}
\label{eq:S_1_constraint}
\lambda = \tan\theta=\frac{n_2R_1}{n_1R_2}=-\frac{m_1R_1}{m_2R_2}
\end{aligned}
\end{equation}
and the conformal boundary state
\begin{equation}\begin{aligned}
\label{eq:S1bd-state}
g_{S_1}\sum_{S_1}e^{in_1\phi_0-im_1\bar{\phi}_0}|n_1,m_1\rangle|n_2,m_2\rangle
\end{aligned}\end{equation}
where $\sum_{S_1}$ is the summation consistent with the constraint in Eq.~\eqref{eq:S_1_constraint}. The g-factor can only be determined by Cardy condition\cite{cardy_boundary_2004}. Since it is not important for what follows, we shall not include the calculation here.

Since $S = S_2$ is effectively $S_1$ on the dual boson, we can expect that it will end up in the same expression as in Eq.~\eqref{eq:S1bd-state}, but with a different constraints on the winding number
\begin{equation}
\vec{M} = \frac{\cot \theta}{g} 
\begin{bmatrix}
0 & -1\\
1 & 0 \\                                
\end{bmatrix}
\vec{M}^*
\end{equation}

\subsection{Winding Mode Contribution to the Partition Function}
\label{app_sub:winding_contribution}
We now calculate the winding mode part of the partition function as shown in Fig.~\ref{fig:fig_lambda_1_lambda_2}
\begin{equation}\begin{aligned}
Z=\langle S_j( \theta_2 )|e^{-\pi H}|S_i(\theta_1 )\rangle\qquad H=\frac{2\pi}{\beta}(L_0+\bar{L}_0)
\end{aligned}\end{equation}
With boundary state, we can simply replace $L_0$($\bar{L}_0$) with $a_0$($\bar{a}_0$).

For the amplitude between the same boundary states $\lambda_1=\lambda_2$, we have the winding mode contribution as
\begin{equation}
\begin{aligned}
\label{eq:Z0}
Z_0 \le  \sum_{S_i} g_{\,\!_{S_i} }g_{\,\!_{S_j} } \exp\Big\{- \frac{4\pi}{\beta} 2 \pi g ( \frac{n_1}{ 4 \pi R_1 g} + \frac{m_1 R_1 }{ 2} )^2 \Big\}
\end{aligned}
\end{equation}
where the equality only is only taken when the two boundary states are identical.

In the limit $\beta\rightarrow\infty$, Eq.~\eqref{eq:Z0} can be approximated by a simple two dimensional integral
\begin{equation}\begin{aligned}
Z_0\approx g_{\,\!_{S_i} }g_{\,\!_{S_j} }\beta\int dxdy\exp\Big\{-8 \pi^2 g ( \frac{x}{ 4 \pi R_1 g} + \frac{y R_1 }{ 2} )^2 \Big\}
\end{aligned}\end{equation}
The winding mode thus can contribute at most a $\ln\beta$ term to the free energy. Compared to the result in App.~\ref{app:gnd_dn_lambda}-\ref{app:lambda_12}, we conclude that the winding mode contribution will not present in the leading order of large $\beta$ limit.

>>>>

Our derivation follows the general multi-component boson constraints in Ref.~\onlinecite{affleck_quantum_2001,oshikawa_boundary_2010}. A review of the detailed parameterization of the states can be found in Ref.~\onlinecite{sakai_entanglement_2008}.

\subsection{Mode Expansion of Compact Boson}
Suppose the boson is compactified as $\phi =  \phi + 2\pi R$, using the notation in Ref.\onlinecite{di_francesco_conformal_1997}, we have the following mode expansion 
\begin{widetext}
\begin{equation}
\label{eq:boson-mode-exp}
\begin{aligned}
\phi( z, \bar{z}) = &\phi_0 -i \left( \frac{n}{4\pi g  R} + \frac{m R }{2} \right)  \ln z + \frac{i}{\sqrt{4\pi g}} \sum_{n\ne 0 } \frac{a_n}{n} z^{-n } -i \left( \frac{n}{4\pi g R} - \frac{m R }{2} \right)  \ln \bar{z} + \frac{i}{\sqrt{4\pi g}} \sum_{n\ne 0 } \frac{\bar{a}_n}{n} \bar{z}^{-n } ,
\end{aligned}
\end{equation}\end{widetext}
where $n,m$ are momentum and winding modes quantum numbers.

In Ref.\onlinecite{di_francesco_conformal_1997}, the quantization is performed on an equal time space. The boundary state we need here however lives on $x = 0$ -- a equal-space slice. We therefore exchange compact the theory in time direction with period $T$, and identify the holomorphic and anti-holomorphic coordinates as 
\begin{equation}
\label{eq:zzbar}
z = \exp( 2 \pi i \frac{t - x}{L}), \qquad \bar{z} = \exp( 2 \pi i \frac{t + x}{L}).
\end{equation}
This corresponds to exchange the $x$ and $t$ in Ref.\onlinecite{di_francesco_conformal_1997}.

We further identify
\begin{equation}
\begin{aligned}
  a_0 &= \sqrt{ 4 \pi g } \left( \frac{n}{4\pi g R} + \frac{m R }{2} \right), \\
   \bar{a}_0 &= \sqrt{ 4 \pi g } \left( \frac{n}{4\pi g R} - \frac{m R }{2} \right),
  \end{aligned}
\end{equation}
to obtain the expression uniform for all the modes
\begin{equation}
\begin{aligned}
i \partial_z \phi =  \sum_n \frac{1}{\sqrt{4\pi g}} a_n z^{-n-1} .
\end{aligned}
\end{equation}

@@

We recall that the gluing condition is written as
\begin{equation}
\begin{aligned}
\label{eq:def_S_in_app}
\begin{pmatrix}
\partial_+\phi^1\\
\partial_-\phi^2
\end{pmatrix}
=S(\theta)
\begin{pmatrix}
\partial_-\phi^1\\
\partial_+\phi^2
\end{pmatrix}.
\end{aligned}
\end{equation}
Upon folding $\phi^2$ to the negative axis, its $\partial_x$ derivative becomes $-\partial_x$, so 
\begin{equation}
\begin{bmatrix}
\partial_{+} \phi^1 \\
\partial_{+} \phi^2 \\
\end{bmatrix}
 = S
\begin{bmatrix}
\partial_{-} \phi^1 \\
\partial_{-} \phi^2 \\
\end{bmatrix}.
\end{equation}
In terms of the holomorphic coordinates defined in Eq.~\eqref{eq:zzbar}, 
\begin{equation}
\partial_{+} = \frac{4\pi i }{T} \bar{z} \partial_{\bar{z}} ,\qquad \partial_{-} = -\frac{4\pi i }{T} z\partial_{z},
\end{equation}
the $S$ matrix establish a relation between the modes
\begin{equation}
\begin{aligned}
\label{eq:def_S_in_app_2}
\sum_{n\in\mathbb{Z}}
\begin{pmatrix}
\bar{a}_n^1\bar{z}^{-n}\\
\bar{a}_n^2\bar{z}^{-n}
\end{pmatrix}
= -S(\theta)
\sum_{n\in\mathbb{Z}}
\begin{pmatrix}
a_n^1{z}^{-n}\\
a_n^2{z}^{-n}
\end{pmatrix}.
\end{aligned}
\end{equation}
At the boundary $x = 0$ $\bar{z}=z^{-1}$, therefore we have
\begin{equation}
\begin{aligned}
a^i_n + (S^{-1}_{ij})\bar{a}^j_{-n}=0.
\end{aligned}
\end{equation}
The solution of the $n \ne 0$ constraints is exactly the boundary state in Eq.~\eqref{eq:bd_state}.

We specialize to $S = S_1$ to solve the $ n = 0$ constraint. We introduce the compactification lattice and its dual\cite{affleck_quantum_2001,oshikawa_boundary_2010}
\begin{equation}
\label{eq:lattice}
\vec{M} = (m_1 2 \pi R_1, m_2 2\pi  R_2)^\top, \quad  \vec{M}^* = (\frac{n_1}{R_1}, \frac{n_2}{R_2})^\top,
\end{equation}
to rewrite the zero mode part as 
\begin{equation}
  a_0^i - S^{-1} _{ij} \bar{a}_{0}^j = 0 \,\, \implies \,\, ( \vec{M} + \frac{1}{g}\vec{M}^* ) = S_1 ( -\vec{M} + \frac{1}{g}\vec{M}^* ),
\end{equation}
which is basically the multi-component boson winding constraints given in \onlinecite{affleck_quantum_2001,oshikawa_boundary_2010}. The solution gives the interface parameter $\lambda$
\begin{equation}
\begin{aligned}
\label{eq:S_1_constraint}
\lambda = \tan\theta=\frac{n_2R_1}{n_1R_2}=-\frac{m_1R_1}{m_2R_2},
\end{aligned}
\end{equation}
and the conformal boundary state
\begin{equation}\begin{aligned}
\label{eq:S1bd-state}
g_{S_1}\sum_{S_1}e^{in_1\phi_0-im_1\bar{\phi}_0}|n_1,m_1\rangle|n_2,m_2\rangle,
\end{aligned}\end{equation}
where $\sum_{S_1}$ is the summation consistent with the constraint in Eq.~\eqref{eq:S_1_constraint}. The g-factor can only be determined by Cardy condition\cite{cardy_boundary_2004}. Since it is not important for what follows, we shall not include the calculation here.

Since $S = S_2$ is effectively $S_1$ on the dual boson, we can expect that it will end up in the same expression as in Eq.~\eqref{eq:S1bd-state}, but with a different constraints on the winding number
\begin{equation}
\vec{M} = \frac{\cot \theta}{g} 
\begin{bmatrix}
0 & -1\\
1 & 0 \\                                
\end{bmatrix}
\vec{M}^*.
\end{equation}

\subsection{Winding Mode Contribution to the Partition Function}
\label{app_sub:winding_contribution}
We now calculate the winding mode part of the partition function as shown in Fig.~\ref{fig:fig_lambda_1_lambda_2}
\begin{equation}\begin{aligned}
Z=\langle S_j( \theta_2 )|e^{-\pi H}|S_i(\theta_1 )\rangle,\qquad H=\frac{2\pi}{\beta}(L_0+\bar{L}_0).
\end{aligned}\end{equation}
With boundary state, we can simply replace $L_0$($\bar{L}_0$) with $a_0$($\bar{a}_0$).

For the amplitude between the same boundary states $\lambda_1=\lambda_2$, we have the winding mode contribution as
\begin{equation}
\begin{aligned}
\label{eq:Z0}
Z_0 \le  \sum_{S_i} g_{\,\!_{S_i} }g_{\,\!_{S_j} } \exp\Big\{- \frac{4\pi}{\beta} 2 \pi g ( \frac{n_1}{ 4 \pi R_1 g} + \frac{m_1 R_1 }{ 2} )^2 \Big\},
\end{aligned}
\end{equation}
where the equality only is only taken when the two boundary states are identical.

In the limit $\beta\rightarrow\infty$, Eq.~\eqref{eq:Z0} can be approximated by a simple two dimensional integral
\begin{equation}\begin{aligned}
Z_0\approx g_{\,\!_{S_i} }g_{\,\!_{S_j} }\beta\int dxdy\exp\Big\{-8 \pi^2 g ( \frac{x}{ 4 \pi R_1 g} + \frac{y R_1 }{ 2} )^2 \Big\}.
\end{aligned}\end{equation}
The winding mode thus can contribute at most a $\ln\beta$ term to the free energy. Compared to the result in App.~\ref{app:gnd_dn_lambda}-\ref{app:lambda_12}, we conclude that the winding mode contribution will not present in the leading order of large $\beta$ limit.

### 2017-06-19 disc.tex
[draft] remove the 1/16 scaling dimension todo; it is clear in notes Eq. (124) why there is a factor of 2
[draft] Punctuation checked, may double check the following eqs. ([draft] Punctuation checked, double check the following eqs. (39), (C3), below (C12), (C27), (D9) .

% analytic results type 1 -> type 2, c/4; 
In the Sec.~\ref{sec_sub:analy_eval}, we have presented the analytic results for the general process (assuming the far end boundary condition $c$ is the same as prior-quench interface $a$) 
\begin{equation}
 S_i( \theta_1 ) \rightarrow S_j( \theta_2 )
\end{equation}
We find that if the conformal interfaces are of different types, i.e. $i \ne j$, the (long time) free energy is always $\frac{1}{4} \ln t$, regardless of the theta angles. The two types of conformal interface do not talk to each other because they impose on different fields. If we treat $S_1$ as a combination of Dirichlet and Neumann boundary conditions imposed on the rotated $\phi$ fields as in Eq.~\eqref{eq:rotation_a_basis}, then $S_2$ imposes one of them on the duel field of $\phi$. In the derivation of the $M$ matrix, these two correspond to the parts of the Lorentz group and can't be connected even by taking singular value of $\lambda$. It is then reasonable to find an universal echo between them. The special value of ${\rm DD} \rightarrow P$ also agrees with the existing general CFT result of completely transparent interface\cite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014}.

@@

\todo[inline]{verify the 1/16 statement in reference. }

@@

This set of boundary conditions can be realized by connecting two compact bosons. There are already numerous theoretical and experimental work on the boundary conditions of a Luttinger liquid\cite{schmeltzer_zero_1999,anfuso_luttinger_2003,voit_bounded_2000,fabrizio_interacting_1995,egger_applying_1998}, which is the universal compact boson theory of the (Bosonized) one-dimensional electron gas\cite{giamarchi_quantum_2015}. For example, gate voltage \cite{egger_applying_1998} may be used to twist the left and right modes of the boson to create a boundary condition interpolating between the normal open and fixed boundary conditions. The interface studied in this paper is a generalization which (in the folding picture) twist the two independent Bosons (two left modes plus two right modes) on the two sides. An X-ray edge singularity experiment in a quantum wire system, which uses ion to switch on and off the boson interfaces should be plausible to detect the exponent found in this paper.

>>>>

% analytic results type 1 -> type 2, c/4; 
In the Sec.~\ref{sec_sub:analy_eval}, we have presented the analytic results for the general process (assuming the far end boundary condition $c$ is the same as prior-quench interface $a$) 
\begin{equation}
 S_i( \theta_1 ) \rightarrow S_j( \theta_2 ),
\end{equation}
We find that if the conformal interfaces are of different types, i.e. $i \ne j$, the (long time) free energy is always $\frac{1}{4} \ln t$, regardless of the theta angles. The two types of conformal interface do not talk to each other because they impose on different fields. If we treat $S_1$ as a combination of Dirichlet and Neumann boundary conditions imposed on the rotated $\phi$ fields as in Eq.~\eqref{eq:rotation_a_basis}, then $S_2$ imposes one of them on the duel field of $\phi$. In the derivation of the $M$ matrix, these two correspond to the parts of the Lorentz group and can't be connected even by taking singular value of $\lambda$. It is then reasonable to find an universal echo between them. The special value of ${\rm DD} \rightarrow P$ also agrees with the existing general CFT result of completely transparent interface\cite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014}.

@@

@@

This set of boundary conditions can be realized by connecting two compact bosons. There are already numerous theoretical and experimental work on the boundary conditions of a Luttinger liquid\cite{schmeltzer_zero_1999,anfuso_luttinger_2003,voit_bounded_2000,fabrizio_interacting_1995,egger_applying_1998}, which is the universal compact boson theory of the (bosonized) one-dimensional electron gas\cite{giamarchi_quantum_2015}. For example, gate voltage \cite{egger_applying_1998} may be used to twist the left and right modes of the boson to create a boundary condition interpolating between the normal open and fixed boundary conditions. The interface studied in this paper is a generalization which (in the folding picture) twist the two independent bosons (two left modes plus two right modes) on the two sides. An X-ray edge singularity experiment in a quantum wire system, which uses ion to switch on and off the boson interfaces should be plausible to detect the exponent found in this paper.

### 2017-06-19 general_formulation.tex
[draft] App. G sign issue fixed.
1. figure font enlarged. 2. name accent fixed in bib 3. captions need to be checked later.
[draft] Punctuation checked, may double check the following eqs. ([draft] Punctuation checked, double check the following eqs. (39), (C3), below (C12), (C27), (D9) .

The general constraint we can impose on an interface is that the momentum flow (or current flow if exists) should be continuous. An equivalent way of viewing it (and will be used later) is to fold one of the theories on top of the other. The interface now located on the boundary of the tensor theory becomes impenetrable, and momentum flow ends there. This folding picture leads to the concept of boundary states in the framework of boundary CFT\cite{cardy_boundary_2004,cardy_conformal_1984}. In the Boson theory we are interested in, the tensor theory has $c = 2$ and the general classification the boundary state is still an open questions\cite{affleck_quantum_2001}.

@@

Assume two free Bosons fields $\phi^1$ and $\phi^2$ live on the left and right half planes respectively. Their interface located at $x = 0$ are characterized by the ``gluing condition"
\begin{equation}\begin{aligned}
\label{eq:def_M}
\begin{pmatrix}
\partial_t\phi^1\\
\partial_x\phi^1
\end{pmatrix}
=M\begin{pmatrix}
\partial_t\phi^2\\
\partial_x\phi^2
\end{pmatrix}
\end{aligned}\end{equation}
where derivative should be understood in the appropriate left and right limits, for example $\partial_x \phi^1$ is evaluated at $ x = 0^-$. As argued, the momentum component of stress tensor is continuous across the interface. As a consequence $M$ is an element of the Lorentz group $O(1,1)$ and can be parameterized as
\begin{equation}\begin{aligned}
\label{eq:M1M2}
M_1(\theta)=\pm
\begin{bmatrix}
\lambda^{-1} & 0 \\
0 & \lambda
\end{bmatrix}\quad
M_2(\theta)=\pm
\begin{bmatrix}
0 & \lambda  \\
\lambda^{-1} & 0 
\end{bmatrix}
\end{aligned}\end{equation}
where $\lambda=\tan\theta$ for $\theta\in\left[-\frac{\pi}{2},\frac{\pi}{2}\right]$.

@@

The physical significance of $\theta$ will be manifest in the scattering process described below. We rewrite the Eq.~\eqref{eq:def_M} in the coordinates $t\pm x$ and use $\partial_{\pm} = \partial_{t} \pm \partial_x $ to extract the left and right going modes. For example, $\partial_{-} \phi^2$ will be a function $t - x$ and hence represents a right going mode on the right half plane. It is then one of the scattering products that leaves the interface. On the other hand $\partial_{-} \phi^1$ and $\partial_{+} \phi^2$ are modes that approaching the interface from their respective domain. We therefore establish the scattering relation 
\begin{equation}\begin{aligned}
\label{eq:def_S}
\begin{pmatrix}
\partial_+\phi^1\\
\partial_-\phi^2
\end{pmatrix}
=S
\begin{pmatrix}
\partial_-\phi^1\\
\partial_+\phi^2
\end{pmatrix}
\end{aligned}\end{equation}
and solve the $S$ matrix for the two cases of $M_1$ and $M_2$
\begin{equation}\begin{aligned}
\label{eq:S1_S2}
S_1(\theta)=\begin{bmatrix}
\cos 2\theta & \sin 2\theta \\
\sin 2\theta & -\cos 2\theta
\end{bmatrix}\quad
S_2(\theta)=\begin{bmatrix}
-\cos 2\theta & \sin 2\theta \\
-\sin 2\theta & -\cos 2\theta
\end{bmatrix}
\end{aligned}\end{equation}
For generic values of $\theta$, the interface is partially-transmitting, whose transmission and reflection coefficients can be read off from the scattering matrices. The fact of their wavelength independence is an indication of scale invariance of the interface.

\begin{figure}[h]
\centering
\includegraphics[width=0.5\textwidth]{fig_folding_pic.pdf}
\caption{Folding picture for penetrable interface. Left panel: World line of the penetrable interface. $\partial_\pm\phi^{1,2}$ denote the left and right going modes in their respective domain. Right panel: Folding operation that sends $\phi^2(x)$ to $\phi^2(-x)$. The dashline represents the \emph{im}penetrable boundary for the resulting tensor theory.}
\label{fig:folding_pic}
\end{figure}

We now work in the folding picture as shown in Fig.~\ref{fig:folding_pic}. The boundary at $x=0$ becomes impenetrable for the folded system, and the resulting tensor theory admits a conformal boundary state. The folding sends $\phi^2(x)$ to $\phi^2(-x)$ and hence the gluing condition becomes
\begin{equation}
\begin{aligned}
\partial_t(\cos\theta\phi^1-\sin\theta\phi^2)=0 \quad
\partial_x(\sin\theta\phi^1+\cos\theta\phi^2)=0 
\end{aligned}
\end{equation}
for the case $M = M_1(\theta)$.

If we quantize the Boson theory on the interface line $x = 0$, these gluing conditions become an operator identity for the boson creation and annihilation of the modes. We shall interpret these identities to be valid only when acting on the boundary states. The mode expansion of free boson on $x = 0$\cite{di_francesco_conformal_1997} is
\begin{equation}
\phi(z, \bar{z} ) = \phi_0 - \frac{i}{4\pi g } \pi_0 \ln z \bar{z}  + \frac{i}{\sqrt{4\pi g} } \sum_{n \ne 0 } \frac{1}{n} \left(a_n z^{-n} + \bar{a}_{n} \bar{z}^{-n}   \right)
\end{equation}
where we take $T$ to be time period and the following choice of the holomorphic and anti-holomorphic coordinates
\begin{equation}
z= e^{ 2\pi i(x - t) / T } \quad \bar{z} = e^{ 2\pi i( x + t  ) / T }
\end{equation}
We end up with a set of operator identities for each mode
\begin{equation}
\begin{aligned}
\label{eq:rotation_a_basis}
\cos\theta a_n^1-\sin\theta a_n^2 &= +( \cos\theta\bar{a}_{-n}^1-\sin\theta \bar{a}_{-n}^2 ) \\
\sin\theta a_n^1+\cos\theta a_n^2 &= -( \sin\theta\bar{a}_{-n}^1+\cos\theta \bar{a}_{-n}^2 ) 
\end{aligned}
\end{equation}
which is valid on the following boundary state
\begin{equation}
\label{eq:bd_state}
\begin{aligned}
| B \rangle 
& =  \exp\Big\{ \sum_{n > 0 } \frac{1}{n}
\begin{pmatrix}
a_{-n}^1\\
a_{-n}^2\\                              
\end{pmatrix}
S_1( \theta )
\begin{pmatrix}
\bar{a}_{-n}^1  \bar{a}_{-n}^2
\end{pmatrix} \Big\} |0\rangle
\end{aligned}
\end{equation}
where $S_1(\theta) $ is precisely the scattering matrix in Eq.~\eqref{eq:def_S}. The calculation for the case $M=M_2(\theta)$ is completely analogous.

>>>>

The general constraint we can impose on an interface is that the momentum flow (or current flow if exists) should be continuous. An equivalent way of viewing it (and will be used later) is to fold one of the theories on top of the other. The interface now located on the boundary of the tensor theory becomes impenetrable, and momentum flow ends there. This folding picture leads to the concept of boundary states in the framework of boundary CFT\cite{cardy_boundary_2004,cardy_conformal_1984}. In the boson theory we are interested in, the tensor theory has $c = 2$ and the general classification the boundary state is still an open questions\cite{affleck_quantum_2001}.

@@

Assume two free bosons fields $\phi^1$ and $\phi^2$ live on the left and right half planes respectively. Their interface located at $x = 0$ are characterized by the ``gluing condition"
\begin{equation}\begin{aligned}
\label{eq:def_M}
\begin{pmatrix}
\partial_t\phi^1\\
\partial_x\phi^1
\end{pmatrix}
=M\begin{pmatrix}
\partial_t\phi^2\\
\partial_x\phi^2
\end{pmatrix},
\end{aligned}\end{equation}
where derivative should be understood in the appropriate left and right limits, for example $\partial_x \phi^1$ is evaluated at $ x = 0^-$. As argued, the momentum component of stress tensor is continuous across the interface. As a consequence $M$ is an element of the Lorentz group $O(1,1)$ and can be parameterized as
\begin{equation}\begin{aligned}
\label{eq:M1M2}
M_1(\theta)=\pm
\begin{bmatrix}
\lambda^{-1} & 0 \\
0 & \lambda
\end{bmatrix},\quad
M_2(\theta)=\pm
\begin{bmatrix}
0 & \lambda  \\
\lambda^{-1} & 0 
\end{bmatrix},
\end{aligned}\end{equation}
where $\lambda=\tan\theta$ for $\theta\in\left[-\frac{\pi}{2},\frac{\pi}{2}\right]$.

@@

The physical significance of $\theta$ will be manifest in the scattering process described below. We rewrite the Eq.~\eqref{eq:def_M} in the coordinates $t\pm x$ and use $\partial_{\pm} = \partial_{t} \pm \partial_x $ to extract the left and right going modes. For example, $\partial_{-} \phi^2$ will be a function $t - x$ and hence represents a right going mode on the right half plane. It is then one of the scattering products that leaves the interface. On the other hand $\partial_{-} \phi^1$ and $\partial_{+} \phi^2$ are modes that approaching the interface from their respective domain. We therefore establish the scattering relation 
\begin{equation}\begin{aligned}
\label{eq:def_S}
\begin{pmatrix}
\partial_+\phi^1\\
\partial_-\phi^2
\end{pmatrix}
=S
\begin{pmatrix}
\partial_-\phi^1\\
\partial_+\phi^2
\end{pmatrix},
\end{aligned}\end{equation}
and solve the $S$ matrix for the two cases of $M_1$ and $M_2$
\begin{equation}\begin{aligned}
\label{eq:S1_S2}
S_1(\theta)=\begin{bmatrix}
\cos 2\theta & \sin 2\theta \\
\sin 2\theta & -\cos 2\theta
\end{bmatrix},\
S_2(\theta)=\begin{bmatrix}
-\cos 2\theta & \sin 2\theta \\
-\sin 2\theta & -\cos 2\theta
\end{bmatrix}.
\end{aligned}\end{equation}
For generic values of $\theta$, the interface is partially-transmitting, whose transmission and reflection coefficients can be read off from the scattering matrices. The fact of their wavelength independence is an indication of scale invariance of the interface.
\begin{figure}[h]
\centering
\includegraphics[width=0.45\textwidth]{fig_folding_pic.pdf}
\caption{Folding picture for penetrable interface. Left panel: World line of the penetrable interface. $\partial_\pm\phi^{1,2}$ denote the left and right going modes in their respective domain. Right panel: Folding operation that sends $\phi^2(x)$ to $\phi^2(-x)$. The dashline represents the \emph{im}penetrable boundary for the resulting tensor theory.}
\label{fig:folding_pic}
\end{figure}

We now work in the folding picture as shown in Fig.~\ref{fig:folding_pic}. The boundary at $x=0$ becomes impenetrable for the folded system, and the resulting tensor theory admits a conformal boundary state. The folding sends $\phi^2(x)$ to $\phi^2(-x)$ and hence the gluing condition becomes
\begin{equation}
\begin{aligned}
\partial_t(\sin\theta\phi^1-\cos\theta\phi^2)=0, \quad
\partial_x(\cos\theta\phi^1+\sin\theta\phi^2)=0, 
\end{aligned}
\end{equation}
for the case $M = M_1(\theta)$.

If we quantize the boson theory on the interface line $x = 0$, these gluing conditions become an operator identity for the boson creation and annihilation of the modes. We shall interpret these identities to be valid only when acting on the boundary states. The mode expansion of free boson on $x = 0$\cite{di_francesco_conformal_1997} is
\begin{eqnarray}\begin{aligned}
\phi(z, \bar{z} ) &= \phi_0 - \frac{i}{4\pi g } \pi_0 \ln z \bar{z} \\
 \quad&+ \frac{i}{\sqrt{4\pi g} } \sum_{n \ne 0 } \frac{1}{n} \left(a_n z^{-n} + \bar{a}_{n} \bar{z}^{-n}   \right),
\end{aligned}\end{eqnarray}
where we take $T$ to be time period and the following choice of the holomorphic and anti-holomorphic coordinates
\begin{equation}
z= e^{ \frac{2\pi i(x - t)}{T} }, \quad \bar{z} = e^{ \frac{2\pi i( x + t  )}{T} }.
\end{equation}
We end up with a set of operator identities for each mode
\begin{equation}
\begin{aligned}
\label{eq:rotation_a_basis}
\sin  \theta a^1_n - \cos \theta a^2_n  &= + \left( \sin  \theta \bar{a}^1_{-n} - \cos \theta \bar{a}^2_{-n} \right),\\
\cos  \theta a^1_n + \sin \theta a^2_n  &= - \left( \cos  \theta \bar{a}^1_{-n} + \sin \theta \bar{a}^2_{-n} \right), 
\end{aligned}
\end{equation}
which is valid on the following boundary state
\begin{equation}
\label{eq:bd_state}
\begin{aligned}
| B \rangle 
& =  \exp\Big\{ -\sum_{n > 0 } \frac{1}{n}
\begin{pmatrix}
a_{-n}^1\\
a_{-n}^2\\                              
\end{pmatrix}
S_1( \theta )
\begin{pmatrix}
\bar{a}_{-n}^1  \bar{a}_{-n}^2
\end{pmatrix} \Big\} |0\rangle,
\end{aligned}
\end{equation}
where $S_1(\theta) $ is precisely the scattering matrix in Eq.~\eqref{eq:def_S}. The calculation for the case $M=M_2(\theta)$ is completely analogous.
